---
title: "Homework 01"
---


## TidyTuesday Section

Explore the week's [TidyTuesday](https://github.com/rfordatascience/tidytuesday) challenge. Develop a research question, then answer it through a short data story with [effective visualization(s)]({{< var effective-viz-url >}}).  Provide sufficient background for readers to grasp your narrative.

The dataset displays all 9 Brazilian companies in the Fortune Global 500, which ranks the world's largest companies by annual revenue. The figures below are given in millions of US dollars and are for the fiscal year 2022.[1] Also listed are the headquarters location, net profit, number of employees worldwide and industry sector of each company.

```{r}
library(tidyverse)
library(ggplot2)
companies <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-01-27/companies.csv')
legal_nature <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-01-27/legal_nature.csv')
qualifications <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-01-27/qualifications.csv')
size <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2026/2026-01-27/size.csv')

```
How does the capital stock of companies vary by company size?

```{r}
size_totals <- companies |>
  group_by(company_size) |>
  summarise(total_capital_stock = sum(capital_stock, na.rm = TRUE))

ggplot(size_totals, 
       aes(x = company_size, 
           y = total_capital_stock, 
           fill = company_size)) +
  geom_col() +
  labs(
    title = "Total Capital Stock by Company Size",
    x = "Company Size",
    y = "Total Capital Stock (USD, millions)"
  )
```

